A re-examination of the role of friction in the original Social Force Model

### 2019-06-22 paper.tex
commit to pull

\textcolor{red}{In the last decades, many microscopic models 
for crowd dynamics were developed. The class of force-based model was introduced by Hirai 
and Tarui (1975) introducing the class of \textit{force based} models 
\cite{Hirai}. These models represent the interaction between 
pedestrians and their environment using different kinds of forces inspired in physical systems. For 
example, Okazaki (1979) modeled the movement of pedestrians as 
a magnetized object immersed a magnetic in field \cite{Okazaki}.}\\

@@

\textcolor{red}{A lot of research has been done using data from the Mecca pilgrimage.
Although in this work we focused on Ref.~\cite{helbing3}. There were several investigations 
using real data to calibrate parameters of the PedFlow model developed by 
L\"ohner et al. Ref.~\cite{lohner2}. Recently a paper was published that uses 
the Kalman filter ensemble to adjust the parameters of this model Ref.~\cite{Togashi1}. 
For more information on PedFlow and Mecca pilgrimage measurements
see Refs.~\cite{Boltes,Dridi1,Dridi2,Baqui1,lohner1} }\\

>>>>

\textcolor{red}{In the last decades, many microscopic models 
for crowd dynamics were developed. The class of force-based model was introduced by Hirai 
and Tarui (1975) introducing the class of \textit{force based} models 
\cite{Hirai}. These models assimilate the interaction between 
pedestrians and their environment using different kinds of forces inspired on physical systems. For 
example, Okazaki (1979) modeled the movement of pedestrians as 
a magnetized object immersed a magnetic in field \cite{Okazaki}.}\\

@@

\textcolor{red}{A lot of research has been done using data from the Mecca pilgrimage.
Although in this work we focused on Ref.~\cite{helbing3}, there were several investigations 
using real data to calibrate parameters of the PedFlow model developed by 
L\"ohner et al. Ref.~\cite{lohner2}. Recently, a paper was published that uses 
the Kalman filter ensemble to adjust the parameters of this model Ref.~\cite{Togashi1}. 
For more information on PedFlow and Mecca pilgrimage measurements
see Refs.~\cite{Boltes,Dridi1,Dridi2,Baqui1,lohner1} }\\
